---
title: "LinearModel"
author: "Marcia D Alarcon"
date: "10/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
require(tidyverse)
require(tigerstats)
```

# Introduction

Form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

## SIMS~ARM Regression

```{r}
plot(SIMS~ARM,data=data)
```

This is a generic scatterplot of sims and arm. It shows the greater the arm force(ARM), the greater the simulation(SIMS). It also shows a positive correlation.

```{r}
cor(SIMS~ARM,data=data)
```

This number is the correlation between SIMS and ARM force. The correlation is the measure of the linear association between two variables.


```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The equation is SIMS = -4.095160 + 0.054563 * ARM


```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 

This scatterplot shows that blue line which is the best linear fit to predict the average of SIMS response would be for any ARM strength. The shaded part is the uncertainty of the line itself. It shows all of the data points of each individuals score and corresponding arm strength. 


```{r}
newData=data.frame(GRIP=94,ARM=88)
predict.lm(model.1,newData,interval="prediction")
```

Fit is the predicted SIMS score when you have an ARM strength of 88. The lwr and the upr are the 95% confidence intervals for predicted SIMS score when ARM is 88.

## SIMS~GRIP Regression

```{r}
plot(SIMS~GRIP,data=data)
```

This is a generic scatterplot of sims and grip. It shows the greater the grip force(GRIP), the greater the simulation(SIMS). It also shows a positive correlation.

```{r}
cor(SIMS~GRIP,data=data)
```

This number is the correlation between SIMS and GRIP force. The correlation is the measure of the linear association between two variables.

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

The equation is SIMS = -4.809675 + 0.045463 * GRIP

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 

This scatterplot shows that blue line which is the best linear fit to predict the average of SIMS response would be for any GRIP strength. The shaded part is the uncertainty of the line itself. It shows all of the data points of each individuals score and corresponding arm strength.

```{r}
newData=data.frame(GRIP=94,ARM=88)
predict.lm(model.2,newData,interval="prediction")
```

Fit is the predicted SIMS score when you have an GRIP strength of 94. The lwr and the upr are the 95% confidence intervals for predicted SIMS score when GRIP is 94.

Comparing the two models:
model1(SIMS~ARM) shows a slightly lower Residual standard error of 1.226 where model2(SIMS~GRIP) is 1.295. model1(SIMS~ARM) shows a slightly higher Adjusted R-squared scored at 0.467 where model2(SIMS~GRIP) scored at 0.4053.

Model1(SIMS~ARM) appears to be slightly better model because it has a lower Residual standard error than model2(SIMS~GRIP) also it has a higher Adjusted R-Squared score then model2(SIMS~GRIP).


## SIM~ARM+GRIP Regression

```{r}
model.3 <- lm(SIMS~ARM + GRIP,data=data)
summary.lm(model.3)
``` 

Model3 appears to be the better model because the adjusted R Squared was higher than model1 or model2, and also scored lower in the Residual standard error than model1 or model2.

```{r}
cor(SIMS~ARM + GRIP,data=data)
```


```{r}
newData=data.frame(GRIP=94,ARM=88)
predict.lm(model.3,newData,interval="prediction")
```

Fit is the predicted SIMS score when you have an GRIP strength of 94 and ARM strength of 88. The lwr and the upr are the 95% confidence intervals for predicted SIMS score when GRIP is 94 and ARM is 88.

## Inferential Test

This is the inferential test called anova to compare models.

$H_0$: There is no difference in how well each model fits the data between models (model1,model3)

$H_A$: There is a difference in how well each model fits the data between models (model1,model3).

```{r}
anova(model.1,model.3)
```

The p-value is 0.000004994.

We reject the Null hypothesis because the p value is so small. There is a difference between model1 and model3, we have statistical evidence that model 3 is better than model2.
